Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2015-03-17 ch-tms/tmspart.tex
post review step -2

\section{Introduction}
\subsection{Properties and Applications of WS$_2$}
Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound. The molecular weight is 249.97 \si{g\per \mole}. Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom} and $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478). Two other crystal structures were found in man-made \ce{WS2}, i.e. 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions of \ce{MoS2} and \ce{WS2} were summarized in Table~\ref{tab:ms2lattice}.
%lattice
\begin{table}[htb]
\centering
\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
\begin{tabular}{lccr}
\toprule
         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
\midrule
Lattice constant & a(\AA) & 3.1604 & 3.171 \\
                 & c(\AA) & 12.295 & 12.359 \\
Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
                      & S-1S (\AA)& 3.11  & 3.14   \\
Between \ce{MS2} layer& S-3S (\AA)& NA  & 3.53   \\
\bottomrule
\end{tabular}
\end{table}
\ce{WS2} can also form tubular nanostructures in a similar way as do carbon nanotubes. The geometrical symmetry group of \ce{WS2} NTs has been reported.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}. This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube. The diameter of a nanotube is given by 
\begin{equation}
d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
\end{equation}
Note that $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where $\cos\pi/3 \times 2 = 1$. In analogy with carbon nanotube, chiral angle $\theta$ is
\begin{equation}
\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
\end{equation}
Chiral angles from the interval $[0,\pi/6]$ is sufficient for all possible tube structures. Tubes $(n,0)$ with zero chiral angle are named as zigzag; tubes $(n,n)$ with $\pi/6$ chiral angle are armchair; consequently, all others are referred as chiral ones with $\theta \in (0,\pi/6)$. Fig.~\ref{fig:ch5ntroll} illustrated basis vectors in the atomic plane of unfolded \ce{WS2} and several nanotube indices.
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_tube1}
\caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
\label{fig:ch5ntroll}
\end{figure}

\subsection{Review of Synthesis Methods of WS$_2$}
Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e. \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well. \citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence, this study recapitulated the main categories of synthesis methods:
\begin{enumerate}
\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere;\footnote{M = Mo, W in this work}
\item Direct decomposition of \ce{MS3};
\item Decomposition of the ammonium salt \ce{(NH4)2MS4};
\item Using CNT as templates, arc discharge, or laser ablation.
\end{enumerate}
Except the aforementioned methods, another important reaction in CVD domain was
\begin{align}
\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
\end{align}
This reaction has been explored by several authors\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}

All these methods can be applied to the growth of TMDC few layer structures, directly or with some modifications. Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs were probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} was thoroughly studied,\cite{Feldman1998} and high yield synthesis approach has been established.\cite{Margolin2004} For \ce{WO3} nanoparticles precursor, it was found that the simultaneous reduction and sulfurization was essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles. During the sulfurization process, remaining oxide core was gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ \gls{cs} planes. Further reaction consumed the \ce{WO_x} core, leading to multi-walled \ce{WS2} NTs. For precursor of \ce{WO3} nanowires, \citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless other reducing agents, e.g. \ce{H2}, are used simultaneously.\cite{Tsirlina1998} This fact highlights that sulfur is rather radical at elevated temperature.

@@

Parallel with the scenario of CNT and graphene, TMDC few layer structures have attracted intensive research efforts recently. These atomic TMDC layers exhibited many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} and became a promising candidate in energy harvesting, optoelectronics, and photocatalytic applications. For scientific research purpose, exfoliation by liquid\cite{Smith2011} or mechanical methods\cite{Lee2010a} can provide sufficient materials, yet CVD synthesis of thickness controllable 2D TMDC is stills highly desired, which holds the greatest potential for high yield production of \ce{MS2}. So this work focused on reviewing the CVD based methods. This study will review literatures to date on both \ce{WS2} films and few layer structures and highlight several typical investigations using different synthesis methods, as summarized in Table~\ref{tab:tmsgrowth}. It is important to note that the synthesis of NTs is relevantly independent of substrates, which is in sharp contrast to the scenario of few layer growth. The \ce{WS2} nucleation and interaction with substrates play dominant roles in the growth of 2D FL structures. Hence, it is reasonable to focus on the \ce{WS2} films growth, which presumably could provide valuable insight into the nucleation process on various substrates.

@@

\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL\cite{Berkdemir2013}. Raman spectra (532 nm) fit included $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation.\cite{Zeng2013a,Zhao2013,Lee2013} However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode. Tentative assignments of multi-phonon bands were summarized in supporting information of Ref.\cite{Zhao2013}. As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used. To gain additional wisdom on \ce{MoS2} growth, this thesis thus summarized the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following. \citeauthor{VanderZande2013} prepared \ce{MoS2} on 285 nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in Refs.\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2 h in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 min oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4 h, 700 \si{\degreeCelsius} hold for 5 min, and 10 sccm \ce{N2} within 2 inch tube. rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors led to hexagonal, 3-point star or irregular polycrystalline structures. The growth setup was similar to those in Ref.\cite{Lee2012b}. The substrate and \ce{MoO3} source distance was critical in determining the growth density. The synthesis strategy in Refs.\cite{Lee2013,Lee2012b} was briefly mentioned as well, where \gls{ptas} treated substrate was found to promote the deposition, while KCl treated substrates did not; small carrier gas flow was preferred (1 sccm \ce{N2}). It was also noted that the \ce{MoS2} flakes morphology seemed more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}. On the other hand, \citeauthor{Najmaei2013} also demonstrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons,\cite{Najmaei2013} which was applied by dispersion and meant to control the source amount. It was found the diffusion of vapor \ce{MoO_{3-x}} was the rate-limiting step in \ce{MoS2} growth. This indicated the amount of source was critical in successful synthesis. The nucleation event was more frequently observed at substrate edges, scratches, or rough surface. Step edges was then intentionally created to facilitate the nucleation. As to the growth dynamics, it was postulated the oxysulfides (\ce{MoOS2} Raman spectra found), as intermediate phase, diffused across the bare substrates and formed triangular domains upon further sulfurization. The optimal growth conditions were 800-850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur.

@@

\subsection{Raman on WS$_2$: Bulk, Few Layer and Nanotube}\label{sec:ntram}

@@

Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode were nearly degenerate in energy. Refractive indices from reflectivity measurement were $n_0$= 3.9 and $n_e$ = 2.5. \citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum was used to explain the rich Raman spectra. \citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 \si{cm^{-1}} was observed, which was assumed to be of two-phonon signal nature and corresponded to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge. \citeauthor{Sourisseau1991} assigned this phonon with non-zero momenta as $LA(K_5)$ type (\gls{la}). The enhancement of the total Raman cross section at excitonic resonance in which excitons served as the intermediate state was stronger compared to that of interband resonance. The strong enhancement at excitonic resonance was attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632 nm$) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which was assigned to \gls{la} and \gls{ta} phonon coupling. This coupling process stemmed from disorder-activated zone boundary phonons. A further discussion on this non-symmetric feature of $A_{1g}$ mode will be continued in section~\ref{sec:ntram}.

>>>>

\section{Introduction}
\subsection{Properties and Applications of Tungsten Disulfide}
Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound. The molecular weight is 249.97 \si{g\per \mole}. Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom} and $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478). Two other crystal structures were found in man-made \ce{WS2}, i.e. 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions of \ce{MoS2} and \ce{WS2} are summarized in Table~\ref{tab:ms2lattice}.
%lattice
\begin{table}[htb]
\centering
\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
\begin{tabular}{lccr}
\toprule
         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
\midrule
Lattice constant & a(\AA) & 3.1604 & 3.171 \\
                 & c(\AA) & 12.295 & 12.359 \\
Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
                      & S-1S (\AA)& 3.11  & 3.14   \\
Between \ce{MS2} layer& S-3S (\AA)& NA  & 3.53   \\
\bottomrule
\end{tabular}
\end{table}
\ce{WS2} can also form tubular nanostructures in a similar way as do carbon nanotubes. The geometrical symmetry group of \ce{WS2} NTs has been reported.\cite{Milosevic2000} The basis/lattice vectors $a_1$ and $a_2$ are defined in transition metal plane with equal length $a_0 \approx 3$ \si{\angstrom}. This monolayered sheet can be rolled up to form a tubular structure when the chiral/translation vector $c = n_1a_1 + n_2a_2$ becomes the circumference of the tube. The diameter of a nanotube is given by 
\begin{equation}
d = \frac{\mid c \mid}{\pi} = \frac{a_0}{\pi}\sqrt{n_1^2 + n_1n_2 + n_2^2}
\end{equation}
Note that $a_1 \cdot a_2 = a_1a_2 \cos\pi/3$, where $\cos\pi/3 \times 2 = 1$. In analogy with carbon nanotube, chiral angle $\theta$ is
\begin{equation}
\theta = \tan^{-1}\frac{\sqrt{3}n_2}{2n_1 + n_2}
\end{equation}
Chiral angles from the interval $[0,\pi/6]$ is sufficient for all possible tube structures. Tubes $(n,0)$ with zero chiral angle are named as zigzag; tubes $(n,n)$ with $\pi/6$ chiral angle are armchair; consequently, all others are referred as chiral ones with $\theta \in (0,\pi/6)$. Fig.~\ref{fig:ch5ntroll} illustrated basis vectors in the atomic plane of unfolded \ce{WS2} and several nanotube indices.
\begin{figure}[htb]
\centering
\includegraphics[width=0.8\textwidth]{ws2_tube1}
\caption[\ce{WS2} nanotube rolling]{\ce{WS2} nanotube rolling}
\label{fig:ch5ntroll}
\end{figure}

\subsection{Review of Synthesis Methods of Tungsten Disulfide}
Shortly after the discovery of \gls{cnt} in 1991,\cite{Iijima1991} its transition metal dichalcogenides (TMDC) counterparts, i.e. \ce{WS2}, was synthesized in 1992.\cite{Tenne1992} In the following decades, other TMDC and several metal oxides nanotubes were demonstrated as well. \citeauthor{Rao2003} did an excellent work to review these inorganic nanotubes.\cite{Rao2003} Hence, this study recapitulated the main categories of synthesis methods:
\begin{enumerate}
\item Reducing \ce{MO3} in \ce{H2} and \ce{H2S} atmosphere;\footnote{M = Mo, W in this work}
\item Direct decomposition of \ce{MS3};
\item Decomposition of the ammonium salt \ce{(NH4)2MS4};
\item Using CNT as templates, arc discharge, or laser ablation.
\end{enumerate}
Except the aforementioned methods, another important reaction in CVD domain was
\begin{align}
\cee{WCl6 + S &\rightarrow WS2 + Cl2S2}\\
\cee{MoCl5 + S &\rightarrow MoS2 + S2Cl2} \\
\cee{S2Cl2 + NaOH &\rightarrow NaCl + S + Na2SO3 + H2O}
\end{align}
This reaction has been explored by several authors\cite{Stoffels1999} and could be used under atmospheric pressure.\cite{Li2004a}

All these methods can be applied to the growth of TMDC few layer structures, directly or with some modifications. Among all the members of TMDC nanotubes, \ce{WS2} and \ce{MoS2} NTs were probably the most well investigated.\cite{Homyonfer1997,Tenne1998,Frey1998,Frey1999,Rothschild2000,Zak2000} The reaction mechanism of \ce{WO3} with \ce{H2}/\ce{H2S} was thoroughly studied,\cite{Feldman1998} and a high yield synthesis approach has been established.\cite{Margolin2004} For \ce{WO3} nanoparticles precursor, it was found that the simultaneous reduction and sulfurization was essential for encapsulation of fullerene like \ce{WS2} structures from the oxide nanoparticles. During the sulfurization process, remaining oxide core was gradually reduced and transformed into an ordered superlattice of $\{ 001 \}$ \gls{cs} planes. Further reaction consumed the \ce{WO_x} core, leading to multi-walled \ce{WS2} NTs. For precursor of \ce{WO3} nanowires, \citeauthor{Feldman1996} proposed that TMDC nanotubes growth began with the reduced \ce{WO3} phases, in particular \ce{W_{18}O_{49}}.\cite{Feldman1996} It is worth noting that \ce{MS2} can be prepared by direct sulfurization from its oxides phase, but reaction \cee{MO3 + Se \rightarrow MSe2} will not proceed unless other reducing agents, e.g. \ce{H2}, are used simultaneously.\cite{Tsirlina1998} This fact highlights that sulfur is chemically radical at elevated temperature.

@@

Parallel with the scenario of CNT and graphene, TMDC few layer structures have attracted intensive research efforts recently. These atomic TMDC layers exhibits many appealing features, i.e., indirect-to-direct band gap transition,\cite{Splendiani2010} and became a promising candidate in energy harvesting, optoelectronics, and photocatalytic applications. For scientific research purpose, exfoliation by liquid\cite{Smith2011} or mechanical methods\cite{Lee2010a} can provide sufficient materials, yet CVD synthesis of thickness controllable 2D TMDC is stills highly desired, which holds the greatest potential for high yield production of \ce{MS2}. So this work focused on reviewing the CVD based methods. This study will review literatures to date on both \ce{WS2} films and few layer structures and highlight several typical investigations using different synthesis methods, as summarized in Table~\ref{tab:tmsgrowth}. It is important to note that the synthesis of NTs is relevantly independent of substrates, which is in sharp contrast to the scenario of few layer growth. The \ce{WS2} nucleation and interaction with substrates play dominant roles in the growth of 2D FL structures. Hence, it is reasonable to focus on the \ce{WS2} films growth, which presumably could provide valuable insight into the nucleation process on various substrates.

@@

\citeauthor{Peimyoo2013} prepared \ce{WS2} on \ce{SiO2}-Si using \ce{WO3} powder and sulfur at 800 \si{\degreeCelsius}, aiming at the light emission studies to clarify several contradictory reports.\cite{Peimyoo2013} Uniform PL intensity was found on the triangular \ce{WS2} flakes, in contrast to previous edge enhanced PL\cite{Berkdemir2013}. Raman spectra (532 nm) fit included $E_{2g}^1(M)$ mode at 343 cm$^{-1}$, according to the phonon dispersion calculation \cite{Molina-Sanchez2011} and experimental observation.\cite{Zeng2013a,Zhao2013,Lee2013} However, none of these experimental reports specifically mentioned $E_{2g}^1(M)$ mode. Tentative assignments of multi-phonon bands were summarized in supporting information of Ref.\cite{Zhao2013}. As to the growth setup, similar tube furnace as in Ref \cite{VanderZande2013} and \cite{Najmaei2013} was used. To gain additional wisdom on \ce{MoS2} growth, this thesis thus summarized the growth strategies in Ref \cite{VanderZande2013} and \cite{Najmaei2013} as following. \citeauthor{VanderZande2013} prepared \ce{MoS2} on 285 nm \ce{SiO2}-Si using \ce{MoO3} and S as precursors.\cite{VanderZande2013} In contrast to the seeding method adopted in Refs.\cite{Lee2013,Lee2012b}, \citeauthor{VanderZande2013} stressed the importance of carefully cleaned substrates\footnote{acetone, 2 h in \ce{H2SO4} and \ce{H2O2} (3:1) and 5 min oxygen plasma} and minimum exposure of precursor to air.\footnote{APCVD, 105 \si{\degreeCelsius} for 4 h, 700 \si{\degreeCelsius} hold for 5 min, and 10 sccm \ce{N2} within 2 inch tube. rapid cooling from 570 \si{\degreeCelsius}} Dirty substrates or old precursors led to hexagonal, 3-point star or irregular polycrystalline structures. The growth setup was similar to those in Ref.\cite{Lee2012b}. The substrate and \ce{MoO3} source distance was critical in determining the growth density. The synthesis strategy in Refs.\cite{Lee2013,Lee2012b} was briefly mentioned as well, where perylene-3,4,9,10-tetracarboxylic acid tetrapotassium salt (PTAS) treated substrate was found to promote the deposition, while KCl treated substrates did not; small carrier gas flow was preferred (1 sccm \ce{N2}). It was also noted that the \ce{MoS2} flakes morphology seemed more uniform in Ref\cite{VanderZande2013} than that in Ref\cite{Lee2012b}. On the other hand, \citeauthor{Najmaei2013} also demonstrated \ce{MoS2} FL growth by sulfurization of \ce{MoO3} nanoribbons,\cite{Najmaei2013} which was applied by dispersion and meant to control the source amount. It was found the diffusion of vapor \ce{MoO_{3-x}} was the rate-limiting step in \ce{MoS2} growth. This indicated the amount of source was critical in successful synthesis. The nucleation event was more frequently observed at substrate edges, scratches, or rough surface. Step edges was then intentionally created to facilitate the nucleation. As to the growth dynamics, it was postulated the oxysulfides (\ce{MoOS2} Raman spectra found), as intermediate phase, diffused across the bare substrates and formed triangular domains upon further sulfurization. The optimal growth conditions were 800-850 \si{\degreeCelsius}, 700 Torr, and sufficient sulfur.

@@

\subsection{Raman on Tungsten Disulfide: Bulk, Few Layer, and Nanotube}\label{sec:ntram}

@@

Lattice vibration of natural \ce{MoS2} crystal was studied by \citeauthor{Wieting1971} using infrared and Raman spectroscopy.\cite{Wieting1971} It was found the $E_{1u}$ IR mode and one $E_{2g}$ Raman mode were nearly degenerate in energy. Refractive indices from reflectivity measurement were $n_0$= 3.9 and $n_e$ = 2.5. \citeauthor{Stacy1985} studied \ce{MoS2} and \ce{WS2} Raman spectra using lasing energy close to the absorption edges.\cite{Stacy1985} Second order scattering from phonon with nonzero momentum was used to explain the rich Raman spectra. \citeauthor{Sourisseau1991} investigated the resonant Raman profiles in 2H-\ce{WS2} using ten different excitation wavelengths.\cite{Sourisseau1991} Dramatic intensity variation at 352 \si{cm^{-1}} was observed, which was assumed to be of two-phonon signal nature and corresponded to an overtone or combination band of phonons with non-zero momenta contributing to indirect gap absorption edge. \citeauthor{Sourisseau1991} assigned this phonon with non-zero momenta as $LA(K_5)$ type (\gls{la}). The enhancement of the total Raman cross section at excitonic resonance in which excitons served as the intermediate state was stronger compared to that of interband resonance. The strong enhancement at excitonic resonance was attributed to the characteristics of excitons in layered materials such as large binding energy, enhanced oscillator strength, and small damping constant.\cite{Zhao2013} \citeauthor{Chung1998} grew \ce{WS2} film using \ce{W(CO)6} and \ce{H2S} precursor.\cite{Chung1998} Raman spectra ($\lambda=632$ nm) on films with non-parallel orientation revealed the presence of shoulder mode under $A_{1g}$, which was assigned to \gls{la} and \gls{ta} phonon coupling. This coupling process stemmed from disorder-activated zone boundary phonons. A further discussion on this non-symmetric feature of $A_{1g}$ mode will be continued in section~\ref{sec:ntram}.
